---
title: "Ames Housing Graph"
output:
  html_document:
    fig_height: 2
    fig_width: 5
  word_document:
    fig_height: 2
    fig_width: 5
---

### My Favorite Graph

```{r message = FALSE, warning = FALSE}
# This tutorial will use the following two packages
library(ggplot2)
library(mosaic)
```

In this tutorial, we will use the  [AmesHousing](http://www.amstat.org/publications/jse/v19n3/decock.pdf) data, which provides information on the sales of individual residential properties in Ames, Iowa from 2006 to 2010. The data set contains 2930 observations, and a large number of explanatory variables involved in assessing home values. A full description of this dataset can be found [here](http://www.amstat.org/publications/jse/v19n3/Decock/DataDocumentation.txt).

```{r}
# The csv file should be imported into rstudio:
AmesHousing <- read.csv("data/AmesHousing.csv")
# str(AmesHousing)
```


Here is my favorite graph of the Ame Housing data.
```{r}
ggplot(data = AmesHousing, aes(x = Year.Remod.Add, y = SalePrice)) + geom_point()  + aes(colour = Fireplaces) + labs(title = "Housing Prices in Ames, Iowa by Remodel Year", x = "Year Remodeled", y = "Sale Price")
```



**Remarks:**

This graph shows a graph of house prices in Ames, Iowa and how the remodel date affects that price. We have colored by number of Fireplaces, and we tend to see that houses with more fireplaces tend to be more expensive.





