---
title: "Ames Housing Graph"
output:
  html_document:
    fig_height: 2
    fig_width: 5
  word_document:
    fig_height: 2
    fig_width: 5
---

### My Favorite Graph

```{r message = FALSE, warning = FALSE}
# This tutorial will use the following two packages
library(ggplot2)
library(mosaic)
```

In this tutorial, we will use the  [AmesHousing](http://www.amstat.org/publications/jse/v19n3/decock.pdf) data, which provides information on the sales of individual residential properties in Ames, Iowa from 2006 to 2010. The data set contains 2930 observations, and a large number of explanatory variables involved in assessing home values. A full description of this dataset can be found [here](http://www.amstat.org/publications/jse/v19n3/Decock/DataDocumentation.txt).

```{r}
# The csv file should be imported into rstudio:
AmesHousing <- read.csv("data/AmesHousing.csv")
# str(AmesHousing)
```


Here is my favorite graph of the Ame Housing data.

```{r}
ggplot(data=AmesHousing) +                         
      geom_histogram(mapping = aes(SalePrice/100000), 
          breaks=seq(0, 7, by = 1), col="red", fill="lightblue") + 
      geom_density(mapping = aes(x=SalePrice/100000, y = (..count..)))  +   
      labs(title="Housing Prices in Ames, Iowa (in $100,000)", 
          x="Sale Price of Individual Homes")   
```

``` {r}
AmesHousingNormal = filter(AmesHousing, Condition.1 == "Norm")

AmesHousingNormal3 = mutate(AmesHousingNormal, TotalSqFt = AmesHousingNormal$Gr.Liv.Area  +  AmesHousingNormal$Total.Bsmt.SF)

AmesHousingNormal4 <- filter(AmesHousingNormal3, TotalSqFt < 3000)

AmesHousingNormal5 <-mutate(AmesHousingNormal4, FireplaceYN = ifelse (Fireplaces==0, "No", "Yes"))

ggplot(data = AmesHousingNormal5, aes(x = TotalSqFt, y = SalePrice/1000)) + geom_point()  + aes(colour = FireplaceYN)  + stat_smooth(method = lm) + labs(title = "Affect of Total Square Feet and Fireplaces on Housing Prices in Ames, Iowa", x = "Total Square Feet", y = "Sale Price (in Thousands)")

```


**Remarks:**
Provide a short description of your work here.






